---
title: "Time Series Analysis"
output: html_notebook
author: "Rishab Sarkar"
---

Try executing this chunk by clicking the *Run* button within the chunk or by placing your cursor inside it and pressing *Ctrl+Shift+Enter*. 
Ref Link: https://trends.google.co.in/trends/explore?date=all&geo=IN&q=national%20anthem,national%20song


```{r}
# importing all the necessary libraries
library(tsibble)
library(tidyverse)
library(plotly)
```

```{r}
# CREATE THE DATAFRAME
data <- read_csv('multiTimeline.csv', col_names = c('month', 'nationa_anthem', 'national_song'))
data <- data_frame(data)
head(data)
```
```{r}
#CHECK FOR NULL VALUES IN THE DF
is.null(data) 
```
```{r}
# PLOT THE DATA TO HAVE A BETTER VISUAL
# national anthem for the year 2004
fig <- plot_ly(data[c(2:13),c(1:3)], x = ~month, y = ~nationa_anthem, type = 'scatter', mode='lines+markers')
fig
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
